### 2019-04-22 monograph/thesis/chapters/introduction.tex
Translated introduction.tex and motivation.tex section's title
Partially translated a new paragraph on introduction.tex and fixed
the usage of - (hyphen) instead of \hyp{} for latex correct
hyphenation.

\lang{%
    But entering the universe of good practices, there are many things for
    discoursing. Nonetheless, in this work is presented the implementation of
    tool called `Object Beautifier', which specifically dedicates on how to
    perform the best layout/display of programming code on the computer screen,
    so that maximize and facilitate the understanding of same
    \cite{automaticSynthesis}.
    Therefore, allowing the programmer to disperse
    more time and efforts thinking about its coding algorithms problem,
    other than trying to decipher the information that is presented
    to it on the screen through infinit different code layouts
    \cite{usingVersionControlData}.
}{%
    Assim,
    este trabalho será focado nas ferramentas disposição ou organização do código,
    também conhecidos como ``Source Code Beautifiers'' ou ``Formatadores de Código''.
    Com isso,
    espera\hyp{}se que o desenvolvimento de códigos demande menos esforços,
    pois o desenvolvedor pode forcar seus esforços pensando mais sobre o problema que está sendo resolvido,
    ao contrário de tentar decifrar o que está escrito em sua frente por meio
    de layouts extravagantes ou incomuns \cite{usingVersionControlData}.
}

\lang{%
    Within this work\s area, we need to also think long and hard about how to
    share the programming code of the programmers among you. Now, the problem of
    human diversity, like all big scientific questions -- how do you explain
    something like that -- It can be broken down into sub-questions. It happens
    many times, which is a good practice for a `Programmer A', is not the same
    to another `Programmer B'. For example, imagine some code where a programmer
    decided to put before each `if' statement, a blank line. It is therefore
    expected that whenever we see a blank line we can potentially find a
    matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention. \cite{aPrettyGoodFormatting}
}{%
    Programação de computadores usualmente não é uma tarefa solitária.
    Muitos projetos podem sempre ser escritos pela mesma pessoa durante toda a vide desse projeto mas,
    o quão grande pode ser um projeto que uma pessoa pode fazer sozinha?
    Poderia uma pessoa escrever sozinha todo o sistema de controle de tráfego aéreo do Estados Unidos?
    Uma vez que precisa-se escrever sistemas computacionais maiores,
    tende-se a colocar vários programadores,
    engenheiros de software, gerentes de projeto, etc,
    para que se possa escrever o sistema computacional requerido
    entro do prazo que dado projeto computacional possui.

@@

    Existem algumas possibilidades,
    uma delas poderia ser que a metade do código escrita pelo `Programador A' estará de um jeito.
    Já a outra metade escrita pelo `Programador B' estará de outro.
    Então,
    que tipos de problema isso poderia causar?
    Uma vez que o código não está mais todo escrito sobre um mesmo padrão,
    certas heurísticas perdem possuem sua taxa de acerto reduzidas ao fazer o reconhecimento de padrões.
    Um exemplo de padrão poderia ser rapidamente identificar onde pode estar uma estrutura de controle
    como `if' ou `for' de acordo com a presença ou não de uma linha em branco antes dela,
    já que a presença de uma linha em branco faz um destacamento maior sendo
    reconhecida como um separador de blocos de código distintos.
    \cite{aPrettyGoodFormatting}.
}

\lang{%
    But again this is something heavily dependent of what each one learning
    through their life time. Imagine another programmer do not liked this rule,
    and when he was writing your code involving an `if', he did not put such
    blank line another programmer is expecting. So when the first programmer
    start reading its the code and look for `if', he will be expecting for blank
    lines before its if\s. But will lose some time searching until realize
    another programmer does not put them, or perhaps he forgot to insert them.
    \cite{quantifyingProgramComprehension}
}{%

\lang{%
    These differences are due to the diversity of ways we learn programming,
    i.e., to the ways we are used to doing coding, as much as the abilities and
    objectives of every programmer developed. Hence, nowadays it becomes a big
    problem because we increasingly need more and more programmers working
    together developing several and diverse computing systems. Where the latter
    is due to the fact of the complexity of computer systems growing
    increasingly, therefore over requiring programmers working and sharing their
    codes and ideas. \cite{howProgrammersRead}
}{%

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain-text' mode. Since for code sharing, it is vital for you
    to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
    which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example. \cite{usingSourceControl}
}{%

@@

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re-writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%

@@

\lang{%
    Talking about the last ideia pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re-adding new lines before each one of your beloved if\s, just because some
    night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
    had just removed them?
}{%

@@

\section{Research Goals}

@@

    }
    \item
    \lang{%
        Define, determine and classify which one are good programming practices and
        perform an in-depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    }{%

@@

\section{Implementation Goals}

@@

\section{Related Works}

>>>>

\lang{%
    But entering the universe of good practices, there are many things for
    discoursing. Nonetheless, in this work is presented the implementation of
    tool called `Object Beautifier', which specifically dedicates on how to
    perform the best layout/display of programming code on the computer screen,
    so that maximize and facilitate the understanding of same
    \cite{automaticSynthesis}.
    Therefore, allowing the programmer to disperse
    more time and efforts thinking about its coding algorithms problem,
    other than trying to decipher the information that is presented
    to it on the screen through infinit different code layouts
    \cite{usingVersionControlData}.
}{%
    Assim,
    este trabalho será focado nas ferramentas disposição ou organização do código,
    também conhecidos como ``Source Code Beautifiers'' ou ``Formatadores de Código''.
    Com isso,
    espera\hyp{}se que o desenvolvimento de códigos demande menos esforços,
    pois o desenvolvedor pode forcar seus esforços pensando mais sobre o problema que está sendo resolvido,
    ao contrário de tentar decifrar o que está escrito em sua frente por meio de layouts extravagantes ou incomuns.
    \cite{usingVersionControlData}
}

\lang{%
    Within this work\s area, we need to also think long and hard about how to
    share the programming code of the programmers among you. Now, the problem of
    human diversity, like all big scientific questions -- how do you explain
    something like that -- It can be broken down into sub\hyp{}questions. It happens
    many times, which is a good practice for a `Programmer A', is not the same
    to another `Programmer B'. For example, imagine some code where a programmer
    decided to put before each `if' statement, a blank line. It is therefore
    expected that whenever we see a blank line we can potentially find a
    matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention. \cite{aPrettyGoodFormatting}
}{%
    Programação de computadores usualmente não é uma tarefa solitária.
    Muitos projetos podem sempre ser escritos pela mesma pessoa durante toda a vide desse projeto mas,
    o quão grande pode ser um projeto que uma pessoa pode fazer sozinha?
    Poderia uma pessoa escrever sozinha todo o sistema de controle de tráfego aéreo do Estados Unidos?
    Uma vez que precisa\hyp{}se escrever sistemas computacionais maiores,
    tende\hyp{}se a colocar vários programadores,
    engenheiros de software, gerentes de projeto, etc,
    para que se possa escrever o sistema computacional requerido
    entro do prazo que dado projeto computacional possui.

@@

    Existem algumas possibilidades,
    uma delas poderia ser que a metade do código escrita pelo `Programador A' estará de um jeito.
    Já a outra metade escrita pelo `Programador B' estará de outro.
    Então,
    que tipos de problema isso poderia causar?
    Uma vez que o código não está mais todo escrito sobre um mesmo padrão,
    certas heurísticas perdem possuem sua taxa de acerto reduzidas ao fazer o reconhecimento de padrões.
    Um exemplo de padrão poderia ser rapidamente identificar onde pode estar uma estrutura de controle
    como `if' ou `for' de acordo com a presença ou não de uma linha em branco antes dela,
    já que a presença de uma linha em branco faz um destacamento maior sendo
    reconhecida como um separador de blocos de código distintos,
    \cite{aPrettyGoodFormatting}
}

\lang{%
    But again this is something heavily dependent of what each one learning
    through their life time. Imagine another programmer do not liked this rule,
    and when he was writing your code involving an `if', he did not put such
    blank line another programmer is expecting. So when the first programmer
    start reading its the code and look for `if', he will be expecting for blank
    lines before its if\s. But will lose some time searching until realize
    another programmer does not put them, or perhaps he forgot to insert them.
    \cite{quantifyingProgramComprehension}
}{%
    E por mais uma vez,
    estas heurísticas são fortemente dependentes do aprendizado de cada programador durante sua vida.
    Imagine um segundo programador que não esta habituado com a heurística de outro,
    e toda vez que ele for ler o código deste terceiro programador,
    ela estará perdido para poder se localizar rapidamente dentro do código.
    E portanto,
    o que isso significa?
    Que ele terá que atentamente ler o código escrito por este terceiro programador,
    uma vez que a sua organização difere dos padrões no qual ele sabe como
    rapidamente se localizar. \cite{quantifyingProgramComprehension}
}

\lang{%
    These differences are due to the diversity of ways we learn programming,
    i.e., to the ways we are used to doing coding, as much as the abilities and
    objectives of every programmer developed. Hence, nowadays it becomes a big
    problem because we increasingly need more and more programmers working
    together developing several and diverse computing systems. Where the latter
    is due to the fact of the complexity of computer systems growing
    increasingly, therefore over requiring programmers working and sharing their
    codes and ideas. \cite{howProgrammersRead}
}{%
    As diferenças entres os diversos estilos de programação entre os programadores deve\hyp{}se à diversos fatores.
    \begin{enumerate}
        \item
        Alguns programadores simplesmente fazem de um determinado jeito
        por que foi assim que ele aprenderam de seus tutores,
        e nunca preocuparam\hyp{}se em questionar se poderia ser feito de outra maneira.
        Uma caso onde isso pode acontecer é devido se ao cansaço que algumas linguagens de
        programação como \latex causam por sua sintaxe incomum e extraordinária.
        Uma vez que você já está cansado de ver tantos errors,
        você simplesmente para de questionar como o texto poderia ser formado e aceita o que
        você encontra escrito e funcionando como parte da sintaxe da linguagem.
        \item
        Outros podem ter determinadas características devido a alguma característica emocional ou física.
        Emocionalmente você pode ``não gostar'' de alguma característica por que sofreu
        algum trauma ou simplesmente esta muito acostumado a ter a ter
        visualmente todos os elementos muito próximos um dos outros na tela.
        Assim,
        mesmo tal característica não ser nada fácil para que outras pessoas entendam o seu código,
        ela pode ser muito fácil de ser compreendida por você,
        que a muitos anos já está habituado a realizar a escrita de seus códigos desta determinada
        forma e portanto é muito hábil e muito rapidamente consegue entender o que escreve.
        \item
        Uma característica física que pode determinar
    \end{enumerate}
    Hoje em dia,
    com a criação de sistemas computacionais cada vez mais complexos,
    torna-se um problema juntar em um único projeto diversos programadores,
    cada um com suas características pessoais distintas.
    \cite{howProgrammersRead}
}

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain\hyp{}text' mode. Since for code sharing, it is vital for you
    to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
    which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example. \cite{usingSourceControl}
}{%

@@

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re\hyp{}writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%

@@

\lang{%
    Talking about the last ideia pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re\hyp{}adding new lines before each one of your beloved if\s, just because some
    night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
    had just removed them?
}{%

@@

\section{\lang{Research Goals}{Objetivos de Pesquisa}}

@@

    }
    \item
    \lang{%
        Define, determine and classify which one are good programming practices and
        perform an in\hyp{}depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    }{%

@@

\section{\lang{Implementation Goals}{Objetivos de Implementação}}

@@

\section{\lang{Related Works}{Trabalhos Relacionados}}
